Plug-and-play dual-tree algorithm runtime analysis

### 2014-11-26 bounds-files/imbalance.tex
Refactor slightly and prepare for some empirical results.

It is well-known that imbalance in trees leads to degradation in performance;
for instance, a $kd$-tree node with every descendant except one in its left
child is effectively useless.  A $kd$-tree full of nodes like this will perform
abysmally for nearest neighbor search, and it is not hard to generate a dataset
that will cause a $kd$-tree of this sort.

@@

\begin{figure}
\begin{center}
  \input{figures/single-outlier-tree.tex}
\end{center}
\label{fig:outlier}
\caption{Single-outlier cover tree.}
\end{figure}

@@

As we will see later empirically, the notion of cover tree imbalance does a good
job of capturing the `goodness' of a tree.  We will use this notion in order to
quantify the worst-case performance of dual-tree algorithms using the cover
tree.

>>>>

It is well-known that imbalance in trees leads to degradation in performance;
for instance, a $kd$-tree node with every descendant except one in its left
child is effectively useless.  A $kd$-tree full of nodes like this will perform
abysmally for nearest neighbor search, and it is not hard to generate a
pathological dataset that will cause a $kd$-tree of this sort.

@@

\begin{figure}
\begin{center}
  \input{figures/single-outlier-tree.tex}
\end{center}
\caption{Single-outlier cover tree.}
\label{fig:outlier}
\end{figure}

@@

For most real-world datasets, the tree imbalance is sublinear in the number of
points.  To demonstrate this, Table \ref{tab:emp_imbalance} shows empirically
calculated cover tree imbalance for cover trees on a number of datasets built
with both the cover tree implementation in {\bf mlpack} \citep{mlpack2013} and
the original reference implementation \citep{langford2006}.

\begin{table}[tb]
\begin{center}
\begin{tabular}{|c|c|c|r|r|}
\hline
Dataset & $N$ & $d$ & reference & mlpack \\
\hline
wine & & & & \\
isolet & & & & \\
corel & & & & \\
mnist & 70000 & 784 & & \\
bio & & & & \\
phy & & & & \\
covertype & & & & \\
LCDM & & & & \\
\hline
\end{tabular}
\end{center}
\caption{Empirical tree imbalance calculations.}
\label{tab:emp_imbalance}
\end{table}
